---
title: "throwaway"
author: "Dan Wigodsky"
date: "October 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(e1071)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(ResourceSelection)
library(gridExtra)
#suppressWarnings(suppressMessages(library(DMwR)))
suppressWarnings(suppressMessages(library(MASS)))
suppressWarnings(suppressMessages(library(car)))
suppressWarnings(suppressMessages(library(corrplot)))
suppressWarnings(suppressMessages(library(pROC)))
suppressWarnings(suppressMessages(library(caret)))
```

```{r, warning=FALSE}
boston_data_set<-read.csv('https://raw.githubusercontent.com/WigodskyD/data-sets/master/crime-training-data.csv')
head(boston_data_set)
boston_data_set %>% 
  mutate(taxrad=tax*rad) %>% 
  mutate(radsq = rad^2) %>% 
  mutate(taxsq = tax^1.7) %>% 
  mutate(indussq = indus^2) %>% 
  mutate(taxradsq = taxrad^2)->boston_data_set
correl.matrix<-cor(boston_data_set, use="complete.obs")
corrplot(correl.matrix,method="color",type="upper")
#plota<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$zn,aes(y=boston_data_set$zn,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='zn')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotb<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$indus,aes(y=boston_data_set$indus,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='indus')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotc<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$chas,aes(y=boston_data_set$chas,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='chas')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotd<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$nox,aes(y=boston_data_set$nox,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='nox')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plote<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$rm,aes(y=boston_data_set$rm,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='rm')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotf<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$age,aes(y=boston_data_set$age,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='age')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotg<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$dis,aes(y=boston_data_set$dis,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='dis')+ theme(panel.background = element_rect(fill = '#4286f4'))
#ploth<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$rad,aes(y=boston_data_set$rad,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='rad')+ theme(panel.background = element_rect(fill = '#4286f4'))
#ploti<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$tax,aes(y=boston_data_set$tax,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='tax')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotj<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$ptratio,aes(y=boston_data_set$ptratio,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='ptrario')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotk<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$lstat,aes(y=boston_data_set$lstat,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='lstat')+ theme(panel.background = element_rect(fill = '#4286f4'))
#plotl<-ggplot()+geom_boxplot(data=boston_data_set, y=boston_data_set$medv,aes(y=boston_data_set$medv,x=boston_data_set$target,group=boston_data_set$target))+labs(x='target',y='medv')+ theme(panel.background = element_rect(fill = '#4286f4'))
#grid.arrange(plota,plotb,plotc,plotd,plote,plotf,plotg,ploth,ploti,plotj,plotk,plotl,nrow = 3)
```

```{r, warning=FALSE,echo=FALSE}
options(expressions= 230000)
set.seed(102)
testing_indices<-sample(1:length(boston_data_set[,1]),(.4*length(boston_data_set$target)))
testing_set<-boston_data_set[testing_indices,]
training_set<-boston_data_set[-testing_indices,]

full_model<-glm(data=training_set,target~zn+indus+chas+nox+rm+age+dis+rad+tax+ptratio+black+lstat+medv)
vif(full_model)
#most_significant_predictors<-training_set[,c(4,6,8,13,14)]
#most_significant_model<-glm(data=most_significant_predictors,target~.)
#summary(most_significant_model)

complicated_model<-glm(data=training_set,target~ nox+ age+ log(taxrad) +(taxrad*log(age)) +taxsq+radsq+medv,  family=binomial(link='logit'))
summary(complicated_model)
ggplot()+geom_point(aes(x=seq_along(resid(complicated_model)),y=resid(complicated_model)),color='blue',shape=9,size=3)+ylim(-1.3,1.3)+ theme(panel.background = element_rect(fill = '#d3dded'))+labs(x='Model 3',y='Residuals')
ggplot()+geom_point(aes(x=seq_along(cooks.distance(complicated_model)),y=cooks.distance(complicated_model)),color='blue',shape=9,size=3)+ theme(panel.background = element_rect(fill = '#d3dded'))+labs(x='Model 3',y="Cook's Distance")

#squares_model<-glm(data=training_set,target~+taxrad+indus+indussq+nox+rad,family=binomial(link='logit'))
#summary(squares_model)
#training_set %>% 
#  mutate(percentage = predict(squares_model,training_set,type='response'))->training_set
#head(training_set)

full_model<-glm(data=training_set,target~zn+nox+age+dis+taxrad+ptratio+black+medv+indussq+taxsq,family=binomial(link='logit'))
summary(full_model)

#full_model<-glm(data=training_set,target~zn+indus +chas+nox+rm #+age+dis+rad+tax+ptratio+black+lstat+medv,family=binomial(link='logit'))
#summary(full_model)


#spare_model<-glm(data=training_set,target~dis+nox,family=binomial(link='logit'))
#summary(spare_model)

```

```{r, warning=FALSE,echo=FALSE,fig.width=7, fig.height=7}
options(expressions= 500000)
plot.a<-ggplot()+geom_point(aes(y=training_set$dis,x=training_set$indus,color=factor(training_set$target)))+labs(x='indus',y='dis',color='target\n')+ theme(panel.background = element_rect(fill = 'white'))
plot.b<-ggplot()+geom_point(aes(y=training_set$dis,x=training_set$nox,color=training_set$target))+labs(x='nox',y='dis',color='target\n')+ theme(panel.background = element_rect(fill = 'white'))
plot.c<-ggplot()+geom_point(aes(y=training_set$dis,x=training_set$age,color=training_set$target))+labs(x='age',y='dis',color='target\n')+ theme(panel.background = element_rect(fill = 'white'))
plot.d<-ggplot()+geom_point(aes(y=training_set$dis,x=training_set$taxrad,color=training_set$target))+labs(x='taxrad',y='dis',color='target\n')+ theme(panel.background = element_rect(fill = 'white'))
grid.arrange(plot.a,plot.b,plot.c,plot.d,nrow = 2)

means_group<-matrix(kmeans(training_set[,c(2,4,6,7,15)],8))
training_set<-cbind(training_set,means_group[1])
colnames(training_set)[20]<-'means_group'
kmeans_model<-glm(data=training_set,target~zn+nox+age+dis+taxrad+ptratio+black+medv+taxsq+means_group,family=binomial(link='logit'))
summary(kmeans_model)
vif(kmeans_model)
means_group<-matrix(kmeans(testing_set[,c(2,4,6,7,15)],8))
testing_set<-cbind(testing_set,means_group[1])
colnames(testing_set)[20]<-'means_group'
prediction_set<-predict(kmeans_model,newdata=testing_set,type='response')
target<-testing_set[,14]
ROC_set<-cbind(target,prediction_set)

roc_function_object<-roc(ROC_set[,1],ROC_set[,2])
plot(roc_function_object)
auc(roc_function_object)
column1<-matrix(unlist(roc_function_object[2]))
column2<-matrix(unlist(roc_function_object[3]))
roc_function_matrix<-as.data.frame(cbind(column1,column2),ncol=2)
colnames(roc_function_matrix)<-c('column1','column2')
roc_function_matrix %>% 
  mutate(mean = .5*(column1+(1-column2))) %>% 
  mutate(euclidean_dist = ((column1-mean)^2+((1-column2)-mean)^2)^.5)->roc_function_matrix
threshold<-(which.max(roc_function_matrix$euclidean_dist))/length(roc_function_matrix[,1])
as.data.frame(ROC_set)  %>% 
  mutate(guess = prediction_set >threshold )->ROC_set
ROC_set$guess[ROC_set$guess ==TRUE]<-1
ROC_set$guess<-as.factor(ROC_set$guess)
ROC_set$target<-as.factor(ROC_set$target)
confusionMatrix(ROC_set$guess,ROC_set$target,positive="1")
#----------------------------------------------
prediction_set<-predict(complicated_model,newdata=testing_set,type='response')
target<-testing_set[,14]
ROC_set<-cbind(target,prediction_set)

roc_function_object<-roc(ROC_set[,1],ROC_set[,2])
plot(roc_function_object)
auc(roc_function_object)
column1<-matrix(unlist(roc_function_object[2]))
column2<-matrix(unlist(roc_function_object[3]))
roc_function_matrix<-as.data.frame(cbind(column1,column2),ncol=2)
colnames(roc_function_matrix)<-c('column1','column2')
roc_function_matrix %>% 
  mutate(mean = .5*(column1+(1-column2))) %>% 
  mutate(euclidean_dist = ((column1-mean)^2+((1-column2)-mean)^2)^.5)->roc_function_matrix
threshold<-(which.max(roc_function_matrix$euclidean_dist))/length(roc_function_matrix[,1])
as.data.frame(ROC_set)  %>% 
  mutate(guess = prediction_set >threshold )->ROC_set
ROC_set$guess[ROC_set$guess ==TRUE]<-1
ROC_set$guess<-as.factor(ROC_set$guess)
ROC_set$target<-as.factor(ROC_set$target)
confusionMatrix(ROC_set$guess,ROC_set$target,positive="1")

